Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-06-30 paper/ifo-singleTone.tex
editor comments section iii

As described in Section~\ref{sec:ifo}, the audio signal is played through a speaker fixed to the back of M2 (see Fig.~\ref{fig:ifo_schematic_webcam}). 
The intensity of the interference pattern is measured at a single point on the screen, indicated by the pink star in Fig.~\ref{fig:interference_pattern}. 
The webcam records video in three color channels; red, blue, and green. 
We use the green channel as an approximation of the total intensity produced by the monochromatic green laser.
The webcam samples at a rate of $30\, {\rm Hz}$, which limits the spectral content of observable signals to less than $15\,{\rm Hz}$, the Nyquist frequency.

@@

In the following section, we use a hidden Markov model technique, commonly used in continuous-wave searches, to recover a signal with a slowly changing frequency.

>>>>

As described in Section~\ref{sec:ifo}, the audio signal is played through a speaker fixed to the back of M2 (see Fig.~\ref{fig:ifo_schematic_webcam}). 
The intensity of the interference pattern is measured at a single point on the screen, indicated by the pink star in Fig.~\ref{fig:interference_pattern}. 
The webcam records video in three color channels: red, blue, and green. 
We use the green channel as an approximation of the total intensity produced by the green laser.
The webcam samples at a rate of $30\, {\rm Hz}$, which limits the spectral content of observable signals to less than $15\,{\rm Hz}$, the Nyquist frequency.

@@
